Charged pion emission from neutron-rich heavy ion collisions for studies on the symmetry energy

### 2020-08-05 chapters_altFormat/ch_data_analysis.tex
added new format

\begin{figure}[!htb]
     \centering
     \begin{subfigure}[b]{0.24\textwidth}
         \centering
         \includegraphics[width=\textwidth]{psa0.png}
         \caption{$\mathrm{1^{st}}$ step of the PSA}
         \label{fig:psa0}
     \end{subfigure}
     \hfill
     \centering
     \begin{subfigure}[b]{0.24\textwidth}
         \centering
         \includegraphics[width=\textwidth]{psa1.png}
         \caption{$\mathrm{2^{nd}}$ iteration}
         \label{fig:psa1}
     \end{subfigure}
     \hfill
      \centering
     \begin{subfigure}[b]{0.24\textwidth}
         \centering
         \includegraphics[width=\textwidth]{psa2.png}
         \caption{$\mathrm{3^{rd}}$ iteration}
         \label{fig:psa2}
     \end{subfigure}
     \hfill
      \centering
     \begin{subfigure}[b]{0.24\textwidth}
         \centering
         \includegraphics[width=\textwidth]{psa3.png}
         \caption{$\mathrm{4^{th}}$ iteration}
         \label{fig:psa3}
     \end{subfigure}
     \hfill
     \centering
     \begin{subfigure}[b]{.5\textwidth}
         \centering
         \includegraphics[width=\textwidth]{psa4.png}
         \caption{Final output of the PSA}
         \label{fig:psa4}
     \end{subfigure}
     \hfill

@@

\begin{comment}
\begin{figure}[ht!]s
\begin{overpic}[width=\linewidth]{fig5.pdf}
\put(61,55){\contour{white}{ PRF${}_{\mathrm{Gaus}}(\lambda)$ eq. \ref{eq:gaus}  }}
\put(61,49){\contour{white}{ PRF${}_{\mathrm{Gatti}}(\lambda)$ eq. \ref{eq:gatti} }}
\end{overpic}
\caption{Experimental pad response function of many events for a crossing angle of $85^{\circ} < \theta \leq 90^{\circ}$.  }
\label{fig:expprf}
\end{figure}
\end{comment}

@@

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{BDC_P_small_angle.pdf} 
        \caption{Compare the momentum before and after including the BDC vertex for tracks with $\theta_{Lab} < \ang{40}$, before the space charge correciton.} \label{fig:mom_S_before}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{BDC_P_large_angle.pdf} 
        \caption{Comparison of the momentum before and after including the BDC vertex for tracks with $\theta_{Lab} > \ang{40}$, before the space charge correction.} \label{fig:mom_L_before}
    \end{subfigure}

    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{BDC_P_aftercor_small_angle.pdf} 
        \caption{Compare the momentum before and after including the BDC vertex for tracks with $\theta_{Lab} < \ang{40}$, after the space charge correction. } \label{fig:mom_S_after}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{BDC_P_aftercor_large_angle.pdf} 
        \caption{Compare the momentum before and after including the BDC vertex for tracks with $\theta_{Lab} < \ang{40}$, after the space charge correction.} \label{fig:mom_L_after}
    \end{subfigure}
\label{fig:mom_sc}
\end{figure}

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{BDC_P_frac_small_angle.pdf} 
        \caption{Generic} \label{fig:mom_S_1D}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{BDC_P_frac_large_angle.pdf} 
        \caption{Competitors} \label{fig:mom_L_1D}
    \end{subfigure}

\label{fig:mom_1D}
\end{figure}
\end{comment}

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\linewidth]{sn132_SC} 
        \caption{$\tin{132}{123}$ system.} \label{fig:132momdist_sc}
    \end{subfigure}

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\linewidth]{sn108_SC} 
        \caption{$\tin{108}{112}$ system.} \label{fig:108momdist_sc}
    \end{subfigure}
\caption{Momentum distributions of the Left and Right sides of the TPC for $\pi^+$ and $\pi^-$ particles.}
\label{fig:sc_momdist}
\end{figure}

@@

\begin{figure}[!htb]
  \begin{center}
    \includegraphics[width=0.33\textwidth]{run2907_yoffset6before_row_at_layer10.png}
    \includegraphics[width=0.33\textwidth]{run2907_yoffset5before_row_at_layer30.png}
    \includegraphics[width=0.33\textwidth]{run2907_yoffset4before_row_at_layer50.png}

    \includegraphics[width=0.33\textwidth]{run2907_yoffset6after_row_at_layer10.png}
    \includegraphics[width=0.33\textwidth]{run2907_yoffset5after_row_at_layer30.png}
    \includegraphics[width=0.33\textwidth]{run2907_yoffset4after_row_at_layer50.png}

  \end{center}
  \caption{Cobo timing correction for three different layers. One singe pad is represented by a unique layer and row number. The $dy$ residual of the track fitting shows, in the upper panel, that there is a timing calibration issue. This offset is fixed over several runs for a given pad. Therefore we can correct using a time correction map for each pad; the bottom panels show the distribution after correction. }
  \label{fig:coboCorr}
\end{figure}

\begin{figure}[!htb]
    \begin{subfigure}[t]{.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{run2905_yoffset1before_all.jpg} 
        \caption{Before applying the timing correction.} \label{fig:yoff_allBefore}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{run2905_yoffset1after_all.png}
        \caption{After applying the timing correction.} \label{fig:yoff_allAfter}
    \end{subfigure}
    \caption{Y-residual distributions for all pads.}
\label{fig:yoff}
\end{figure}

@@

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{mcresponse.png}
        \caption{200 MeV/c $\pi^-$ MC digitized track} \label{fig:mcevent}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{event5.png} 
        \caption{Experimental data event.} \label{fig:dataevent}
    \end{subfigure}
    \caption{Charge readout of the pad plane, showing the max ADC in a given pad, for both the MC simulation and experimental data.}
\label{fig:mcDataEmbedtrack}
\end{figure}

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{perspective_embed}
        \caption{Perspective view.} \label{fig:persEmbed}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\linewidth]{top_embed} 
        \caption{Top down view.} \label{fig:topEmbed}
    \end{subfigure}
     \hfill
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\linewidth]{side_embed} 
        \caption{Side view.} \label{fig:sideEmbed}
    \end{subfigure}
    \caption{A 200 MeV/c $\pi^-$ embedded into a nuclear collision type event. The embedded track identified by the software is highlighted by the solid green line. }

\label{fig:embedtrack}
\end{figure}

@@

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{deltaE_topview_neg} 
        \caption{Top view} \label{fig:deltaE_topview}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{deltaE_sideview_neg} 
        \caption{Side view} \label{fig:deltaE_sideview}
    \end{subfigure}
    \caption{Geant4 simulation of ${}^{108}$Sn beam at 270 MeV/A in P10 gas. Notice the extent of the delta electrons in the vertical direction as compared to the horizontal extent. }
\label{fig:deltaE}
\end{figure}

@@

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{pim_200_pol.png}
        \caption{Polar efficiency plot where $\theta$ is represented by the radius of the circle and $\phi$ is measured as the polar angle made between the y and x axis; this view is  best understood as looking at the TPC from the downstream point of view.} \label{fig:pim_pol_eff_ex}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{pim_200_efficiency.png} 
        \caption{Cartesian representation of the same efficiency plot  as in the polar plot.} \label{fig:pim_flat_eff_ex}
    \end{subfigure}

\caption{Efficiency calculations for $\pi^-$ particle traveling at \SI{200}{\mega\eVperc}.}
\label{fig:pim_eff_ex}
\end{figure}

@@

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{pim_132_efficiency.png}
        \caption{$\pi^-$ efficiency for $\tin{132}{124}$} \label{fig:pim_132_eff}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{pip_132_efficiency.png} 
        \caption{$\pi^+$ efficiency for $\tin{132}{124}$} \label{fig:pip_132_eff}
    \end{subfigure}

    \caption{Pion efficiencies in the $\tin{132}{124}$ system. }
\label{fig:132_eff}
\end{figure}

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{pim_132_efficiency.png}
        \caption{$\pi^-$ efficiency for $\tin{108}{112}$} \label{fig:pim_108_eff}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{pip_108_efficiency.png} 
        \caption{$\pi^+$ efficiency for $\tin{108}{112}$} \label{fig:pip_108_eff}
    \end{subfigure}

    \caption{ Pion efficiencies in the $\tin{108}{112}$ system. }
\label{fig:108_eff}
\end{figure}

@@

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{pidPion.png}
        \caption{Output PID pions.} \label{fig:pidpion_raw}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{pidPion_zi.png} 
        \caption{PID plot for $\pi^-$ and $\pi^+$ species in $z_i$. } \label{fig:pipion_zi}
    \end{subfigure}

    \caption{The charged pion PID plot achieved in the $\tin{132}{124}$ system. PID is achieve by plotting $\langle dE/dx\rangle$ versus particle rigidity, $p/q$. Unique hyperbolic lines show different particle species, where negatively charged particles are plotted as negative rigidity.  }
\label{fig:pidpion}
\end{figure}

@@

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{pim_mom2.png}
        \caption{Bin -54 MeV/c < p/q < -52. } \label{fig:pimmom2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{pim_mom1.png} 
        \caption{Bin -68 MeV/c < p/q < -66.} \label{fig:pimmom1}
    \end{subfigure}

@@

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{pip_mom1.png}
        \caption{Bin 74 MeV/c < p/q < 76. } \label{fig:pipmom1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{pip_mom2.png} 
        \caption{Bin 94 MeV/c < p/q < 86.} \label{fig:pipmom2}
    \end{subfigure}

    \caption{Flattened PID $z_i$ distribution  for binned slices in p/q around the $\pi^+$.}
\label{fig:pipmom_flat}
\end{figure}

>>>>

\begin{figure}[!htb]%
    \centering
    \subfloat[$\mathrm{1^{st}}$ step of the PSA]{{\includegraphics[width=.4\textwidth,valign=t]{psa0.png} \label{fig:psa0}}}%
    \qquad
    \subfloat[$\mathrm{2^{nd}}$ iteration]{{\includegraphics[width=.24\textwidth,valign=c]{psa1.png} \label{fig:psa1}}}%
    \subfloat[$\mathrm{3^{nd}}$ iteration]{{\includegraphics[width=.24\textwidth,valign=c]{psa2.png} \label{fig:psa2}}}%
    \subfloat[$\mathrm{4^{nd}}$ iteration]{{\includegraphics[width=.24\textwidth,valign=c]{psa3.png} \label{fig:psa3}}}%
    \subfloat[Final output of the PSA]{{\includegraphics[width=.24\textwidth,valign=c]{psa4.png} \label{fig:psa}}}%

@@

\begin{figure}[ht!]s
\begin{overpic}[width=\linewidth]{fig5.pdf}
\put(61,55){\contour{white}{ PRF${}_{\mathrm{Gaus}}(\lambda)$ eq. \ref{eq:gaus}  }}
\put(61,49){\contour{white}{ PRF${}_{\mathrm{Gatti}}(\lambda)$ eq. \ref{eq:gatti} }}
\end{overpic}
\caption{Experimental pad response function of many events for a crossing angle of $85^{\circ} < \theta \leq 90^{\circ}$.  }
\label{fig:expprf}
\end{figure}

@@

\begin{figure}[!htb]%
    \centering
    \subfloat[Compare the momentum before and after including the BDC vertex for tracks with $\theta_{Lab} < \ang{40}$, before the space charge correciton.]{{\includegraphics[width=.45\textwidth,valign=c]{BDC_P_small_angle.pdf} \label{fig:psa0}}}%
    \qquad
    \subfloat[Comparison of the momentum before and after including the BDC vertex for tracks with $\theta_{Lab} > \ang{40}$, before the space charge correction.]{{\includegraphics[width=.45\textwidth,valign=c]{BDC_P_large_angle.pdf} \label{fig:mom_L_before}}}\\
    \subfloat[Compare the momentum before and after including the BDC vertex for tracks with $\theta_{Lab} < \ang{40}$, after the space charge correction.]{{\includegraphics[width=.45\textwidth,valign=c]{BDC_P_aftercor_small_angle.pdf} \label{fig:mom_S_after}}}%
    \qquad
    \subfloat[Compare the momentum before and after including the BDC vertex for tracks with $\theta_{Lab} < \ang{40}$, after the space charge correction.]{{\includegraphics[width=.45\textwidth,valign=c]{BDC_P_aftercor_large_angle.pdf}  \label{fig:mom_L_after}}}%

 \label{fig:mom_sc}
\end{figure}

\begin{figure}[!htb]%
    \centering
    \subfloat[$\tin{132}{123}$ system.]{{\includegraphics[width=\textwidth,valign=c]{sn132_SC} \label{fig:132momdist_sc}}}%
    \qquad
    \subfloat[$\tin{108}{112}$ system.]{{\includegraphics[width=\textwidth,valign=c]{sn108_SC} \label{fig:108momdist_sc}}}%
	\caption{Momentum distributions of the Left and Right sides of the TPC for $\pi^+$ and $\pi^-$ particles.}
	\label{fig:sc_momdist}
\end{figure}

@@

\begin{figure}[!htb]%
    \centering
    \subfloat[]{{\includegraphics[width=.3\textwidth,valign=c]{run2907_yoffset6before_row_at_layer10.png} \label{}}}%
    \qquad
    \subfloat[]{{\includegraphics[width=.3\textwidth,valign=c]{run2907_yoffset5before_row_at_layer30.png} \label{}}}%
    \subfloat[]{{\includegraphics[width=.3\textwidth,valign=c]{run2907_yoffset4before_row_at_layer50.png} \label{}}}%\\

    \subfloat[]{{\includegraphics[width=.3\textwidth,valign=c]{run2907_yoffset6after_row_at_layer10.png} \label{}}}%
	\qquad
    \subfloat[]{{\includegraphics[width=.3\textwidth,valign=c]{run2907_yoffset5after_row_at_layer30.png} \label{}}}%
    \subfloat[]{{\includegraphics[width=.3\textwidth,valign=c]{run2907_yoffset4after_row_at_layer50.png} \label{}}}%

	\caption{Cobo timing correction for three different layers. One singe pad is represented by a unique layer and row number. The $dy$ residual of the track fitting shows, in the upper panel, that there is a timing calibration issue. This offset is fixed over several runs for a given pad. Therefore we can correct using a time correction map for each pad; the bottom panels show the distribution after correction. }
  	\label{fig:coboCorr}
\end{figure}

\begin{figure}[!htb]%
    \centering
    \subfloat[Before applying the timing correction.]{{\includegraphics[width=.46\textwidth,valign=c]{run2905_yoffset1before_all.jpg} \label{fig:yoff_allBefore}}}%
    \qquad
    \subfloat[After applying the timing correction.]{{\includegraphics[width=.46\textwidth,valign=c]{run2905_yoffset1after_all.png} \label{fig:yoff_allAfter}}}%

    \caption{Y-residual distributions for all pads.}
	\label{fig:yoff}
\end{figure}

@@

\begin{figure}[!htb]%
    \centering
    \subfloat[200 MeV/c $\pi^-$ MC digitized track]{{\includegraphics[width=.46\textwidth,valign=c]{mcresponse.png} \label{fig:mcevent}}}%
    \qquad
    \subfloat[Experimental data event.]{{\includegraphics[width=.46\textwidth,valign=c]{event5.png} \label{fig:dataevent}}}%
    \caption{Charge readout of the pad plane, showing the max ADC in a given pad, for both the MC simulation and experimental data.}
	\label{fig:mcDataEmbedtrack}
\end{figure}

\begin{figure}[!htb]%
    \centering
    \subfloat[Perspective view.]{{\includegraphics[width=.5\textwidth,valign=c]{perspective_embed} \label{fig:persEmbed}}}%
    \qquad
    \subfloat[Top down view.]{{\includegraphics[width=.3\textwidth,valign=c]{top_embed} \label{fig:topEmbed}}}%
    \subfloat[Side view.]{{\includegraphics[width=.55\textwidth,valign=c]{side_embed} \label{fig:sideEmbed}}}%

    \caption{A 200 MeV/c $\pi^-$ embedded into a nuclear collision type event. The embedded track identified by the software is highlighted by the solid green line. }
	\label{fig:embedtrack}
\end{figure}

@@

\begin{figure}[!htb]%
    \centering
    \subfloat[Top view]{{\includegraphics[width=.46\textwidth,valign=c]{deltaE_topview_neg} \label{fig:deltaE_topview}}}%
    \qquad
    \subfloat[Side view]{{\includegraphics[width=.46\textwidth,valign=c]{deltaE_sideview_neg} \label{fig:deltaE_sideview}}}%

  	 \caption{Geant4 simulation of ${}^{108}$Sn beam at 270 MeV/A in P10 gas. Notice the extent of the delta electrons in the vertical direction as compared to the horizontal extent. }
	\label{fig:deltaE}
\end{figure}

@@

 \begin{figure}[!htb]%
    \centering
    \subfloat[Polar efficiency plot where $\theta$ is represented by the radius of the circle and $\phi$ is measured as the polar angle made between the y and x axis; this view is  best understood as looking at the TPC from the downstream point of view.]{{\includegraphics[width=.46\textwidth,valign=c]{pim_200_pol.png} \label{fig:pim_pol_eff_ex}}}%
    \qquad
    \subfloat[Cartesian representation of the same efficiency plot  as in the polar plot.]{{\includegraphics[width=.46\textwidth,valign=c]{pim_200_efficiency.png} \label{fig:pim_flat_eff_ex}}}%
	\caption{Efficiency calculations for $\pi^-$ particle traveling at \SI{200}{\mega\eVperc}.}
	\label{fig:pim_eff_ex}
\end{figure}

@@

\begin{figure}[!htb]%
    \centering
    \subfloat[$\pi^-$ efficiency for $\tin{132}{124}$]{{\includegraphics[width=.46\textwidth,valign=c]{pim_132_efficiency.png} \label{fig:pim_132_eff}}}%
    \qquad
    \subfloat[$\pi^+$ efficiency for $\tin{132}{124}$]{{\includegraphics[width=.46\textwidth,valign=c]{pip_132_efficiency.png} \label{fig:pip_132_eff}}}%
    \caption{Pion efficiencies in the $\tin{132}{124}$ system. }
	\label{fig:132_eff}
\end{figure}

\begin{figure}[!htb]%
    \centering
    \subfloat[$\pi^-$ efficiency for $\tin{108}{112}$]{{\includegraphics[width=.46\textwidth,valign=c]{pim_132_efficiency.png} \label{fig:pim_108_eff}}}%
    \qquad
    \subfloat[$\pi^+$ efficiency for $\tin{108}{112}$]{{\includegraphics[width=.46\textwidth,valign=c]{pip_108_efficiency.png} \label{fig:pip_108_eff}}}%
 	\caption{ Pion efficiencies in the $\tin{108}{112}$ system. }
	\label{fig:108_eff}
\end{figure}

@@

\begin{figure}[!htb]%
    \centering
    \subfloat[Output PID pions.]{{\includegraphics[width=.46\textwidth,valign=c]{pidPion.png} \label{fig:pidpion_raw}}}%
    \qquad
    \subfloat[PID plot for $\pi^-$ and $\pi^+$ species in $z_i$. ]{{\includegraphics[width=.46\textwidth,valign=c]{pidPion_zi.png} \label{fig:pipion_zi}}}%
 	\caption{The charged pion PID plot achieved in the $\tin{132}{124}$ system. PID is achieve by plotting $\langle dE/dx\rangle$ versus particle rigidity, $p/q$. Unique hyperbolic lines show different particle species, where negatively charged particles are plotted as negative rigidity.  }
	\label{fig:pidpion}
\end{figure}

@@

\begin{figure}[!htb]%
    \centering
    \subfloat[Bin -54 MeV/c < p/q < -52. ]{{\includegraphics[width=.46\textwidth,valign=c]{pim_mom2.png} \label{fig:pimmom2}}}%
    \qquad
    \subfloat[Bin -68 MeV/c < p/q < -66.]{{\includegraphics[width=.46\textwidth,valign=c]{pim_mom1.png} \label{fig:pimmom1}}}%

@@

\begin{figure}[!htb]%
    \centering
    \subfloat[Bin 74 MeV/c < p/q < 76.]{{\includegraphics[width=.46\textwidth,valign=c]{pip_mom1.png} \label{fig:pipmom1}}}%
    \qquad
    \subfloat[Bin 94 MeV/c < p/q < 86.]{{\includegraphics[width=.46\textwidth,valign=c]{pip_mom2.png} \label{fig:pipmom2}}}%
 	\caption{Flattened PID $z_i$ distribution  for binned slices in p/q around the $\pi^+$.}
	\label{fig:pipmom_flat}
\end{figure}
